GSoC 2014 info session - phpMyAdmin

### 2014-02-26 phpmyadmin/GSoC_infosession_05Mar2014/presentation.tex
update previous project list

    \frametitle{What made it into 3.5}
      \item improved support for stored routines, events and triggers
      \item improved ENUM/SET editor
      \item advisor : suggestions to tweak config setting in order to optimise MySQL server performance
      \item zoom search
      \item grid editing
    \frametitle{What made it into 4.0}

@@

@@

      \item new navigation tree

@@

    Full list : \href{http://wiki.phpma.org/pma/GSoC\_2014\_Ideas\_List}{wiki.phpma.org/pma/GSoC\_2014\_Ideas\_List}

@@

      \item Error reporting

@@

@@

    \frametitle{What happens after GSoC}

>>>>

    \frametitle{Successful projects in previous editions}

@@

      \item advisor to optimise MySQL server performance
      \item interface improvements : zoom search, grid editing, new navigation tree, \ldots

@@

      \item AJAX error reporting 

@@

    Full list :
    \href{http://wiki.phpmyadmin.net/pma/GSoC\_2014\_Ideas\_List}{wiki.phpmyadmin.net/pma/GSoC\_2014\_Ideas\_List}

@@

@@

      \item error reporting improvements

@@

    \frametitle{After GSoC}
